New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-15 paper/paper.Rmd
typos

The problem with \textcolor{red}{the} new simple method is that it is not faithful to the precise values for $V_m$ because the orthonormalisation will change them. \textcolor{red}{Even though these changes are for the most part imperceptible, one may wits to remove them and} there are numerous ways that this can be enforced, and details are given in the Appendix.
\textcolor{red}{While they all enforce the same position for the selected variable, they differ in how the remaining variables are adjusted during orthonormalisation.}

>>>>

The problem with \textcolor{red}{the} new simple method is that it is not faithful to the precise values for $V_m$ because the orthonormalisation will change them. \textcolor{red}{Even though these changes are for the most part imperceptible, one may wish to avoid them and} there are numerous ways that this can be enforced, a few are detailed in the Appendix.
\textcolor{red}{While they all enforce the same position for the selected variable, they differ in how the remaining variables are adjusted during orthonormalisation.}

### 2022-09-15 paper/paper.tex
typos

Mathematica provides much utility and versatility, such as inbuilt data
visualisation, data manipulation and analysis, dynamic functionality,
and symbolic and numeric computation. Most of this inbuilt functionality
is quite user-friendly and can be found in the Mathematica
documentation; typically, numerous examples are provided within the
documentation, and some possible issues are outlined there. Also, it is
relatively simple to create dynamic objects via the inbuilt commands
\texttt{Manipulate} or \texttt{DynamicModule}. Control objects, such as
sliders, locator panes, and input fields, can then be used on dynamic
variables, and when there is a change in the dynamic variable the
dynamic objects which contain that dynamic variable will be updated.
This is the essential ingredient for this implementation of the manual
tour. However, it can be hard to alter the behaviour of the control
objects such as setting the 1D slider on a different scale (Slider
increments add 10 points into the slice rather than increasing the slice
height by 0.1 for example).
\textcolor{red}{but this is no longer true if you replace it with animate??}
\textcolor{red}{Alex, is this still true with the controls you are using now?}

The examples presented in the penguins' notebooks all utilise our
primary new function, \texttt{SliceDynamic}. This function typically
accepts grouped data in the form of a matrix where the second last
column details the name of the group and the last column details the
group index
\textcolor{red}{(which can be one if there is only one group)}. After
specifying the initial slice thickness and the slice range, the user is
then presented with an interactive display in which the control objects
appear on the left and the slice visulisation appears on the right. The
user can change the orientation of the slice via the locator pane, which
changes the projection matrix; a slider controls the slice thickness;
and there is an input field, which changes the slice centre. The user
can also change the appearance of the plot by zooming into the center or
changing the point size with sliders
provided.\textcolor{red}{this zoom doesn't work very well} The current
projection can be displayed to contrast it with the slice by ticking a
box. The explicit projection matrix can also be displayed via another
checkbox in order to store it for further study.

>>>>

Mathematica provides much utility and versatility, such as inbuilt data
visualisation, data manipulation and analysis, dynamic functionality,
and symbolic and numeric computation. Most of this inbuilt functionality
is user-friendly and described in the Mathematica documentation;
typically, numerous examples are provided within the documentation, and
some possible issues are outlined there.

Importantly for our work, it is relatively simple to create dynamic
objects via the inbuilt commands \texttt{Manipulate} or
\texttt{DynamicModule}. Control objects, such as sliders, locator panes,
and input fields, can then be used on dynamic variables, and when there
is a change in the dynamic variable the dynamic objects which contain
that variable will be updated. This is the essential ingredient for this
implementation of the manual tour.

However, it can be hard to alter the behaviour of the control objects
such as setting the 1D slider on a different scale (Slider increments
add 10 points into the slice rather than increasing the slice height by
0.1 for example).
\textcolor{red}{but this is no longer true if you replace it with animate??}
\textcolor{red}{Alex, is this still true with the controls you are using now?}

\textcolor{red}{Ursula: this comment about slider scale seems to specific, can we have a more general comment about difficulties, e.g. I remember some issues with the color mapping? Also there seem to be a lot of loops needed? Can you explain what the locator pane is?}

The examples presented in the penguins' notebooks all use our primary
new function, \texttt{SliceDynamic}. This function typically accepts
grouped data in the form of a matrix where the second last column
details the name of the group and the last column details the group
index \textcolor{red}{(which can be one if there is only one group)}.
After specifying the initial slice thickness and the slice range, the
user is presented with an interactive display in which the control
objects appear on the left and the slice visulisation appears on the
right. The user can change the orientation of the slice via the locator
pane, which changes the projection matrix; a slider controls the slice
thickness; and there is an input field, which changes the slice centre.
The user can also change the appearance of the plot by zooming into the
center or changing the point size with sliders
provided.\textcolor{red}{this zoom doesn't work very well} The projected
data can be displayed to contrast it with the slice by ticking a box.
The explicit projection matrix can also be displayed via another
checkbox. This is especially useful when we wish to import a projection
that was identified as interesting in the manual exploration later, as
shown in the applications below.

\textcolor{red}{Details about the implementation and usage instructions are given in the Appendix.}
